%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Additional experience}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
  {Internship} % Job title
  {University of Ulm} % Organization
  {Ulm, Germany} % Location
  {March. 2026 - May. 2026} % Date(s)
  {
    \begin{cvitems}
    \item {Co-authored a paper on abstract interpretation for R
        vectors, defining formal semantics for
        vector operations with support for positive/negative/logical
      indexing, recycling rules, and NA handling.}
    \item {Designed and implemented abstract operations for vector
        manipulation (recycle, select, update) with proper handling of
      must/may attributes, enabling precise static analysis of R code.}
    \item {Implemented the vector abstract domain in flowR (available
          at
      \url{https://github.com/manueldiagostino/flowr/tree/r-vectors/src/abstract-interpretation/vector}).}
    \end{cvitems}
  }

  \cventry
  {Tutor (Logic and Discrete Structures)}
  {University of Parma}
  {Parma, Italy}
  {Sep. 2025 - Jan. 2026}
  {
    \begin{cvitems}
    \item Academic support: provide assistance to first-year
      undergraduate students in understanding the theoretical
      concepts of logic and discrete mathematics.
    \item Practical exercises: guide students in solving problems
      related to set theory, algebraic structures, natural and
      structural induction, as well as propositional and predicate
      logic, helping them consolidate the necessary practical skills.
    \item Providing resources: offer supplementary materials and
      useful resources for further exploration of the topics covered
      in the course (available at
      \url{https://github.com/unipr-org/tutorati/tree/main/EdL}).
    \end{cvitems}
  }

  \cventry
  {Tutor (Algorithms and Data Structures)} % Job title
  {University of Parma} % Organization
  {Parma, Italy} % Location
  {Feb. 2025 - June 2025} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item Conceptual support: assist students in understanding
      fundamental algorithmic concepts, data structures, and their applications.
    \item Problem-solving sessions: guide students through exercises
      involving sorting, recursion, dynamic programming, and common
      data structures like stacks, queues, linked lists, trees, and graphs.
    \item Supplementary materials: provide additional learning
      materials and practical examples to reinforce comprehension
      (available at \url{https://github.com/unipr-org/tutorati/tree/main/ASD}).
    \end{cvitems}
  }

  \cventry
  {Tutor (Logic and Discrete Structures)} % Job title
  {University of Parma} % Organization
  {Parma, Italy} % Location
  {Sep. 2024 - Jan. 2025} % Date(s)
  { \hfill }

  \cventry
  {Internship} % Job title
  {University of Parma} % Organization
  {Parma, Italy} % Location
  {Oct. 2023 - Jan. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Examined the Mopsa static analyzer
        (\url{https://mopsa.lip6.fr/}) through a series of benchmarks
      (coreutils-benchmarks, juliet-benchmarks).}
    \item {Integrated the PPLite library
      (\url{https://github.com/ezaffanella/PPLite}) into the framework.}
    \item {Created a docker container to automate the installation
      (\texttt{manueldiagostino/mopsa:pplite}).}
    \end{cvitems}
  }

\end{cventries}
